---
title: "HW_03_nj2208"
author: "James Ng"
date: "10/12/2019"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(rvest)
library(httr)
knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
theme_set(theme_minimal() + theme(legend.position = "bottom"))
```

## Problem 1

```{r problem 1 code}
library(p8105.datasets)
data("instacart")
```

### 1a.
The data set is a dataframe of `r ncol(instacart)` variables and `r nrow(instacart)` observations. The data frame describes the items available for ordering, their departments and the time of day that they get ordered.

```{r problem 1b code}
dept=instacart %>% 
  as_tibble %>% 
  select(order_id:add_to_cart_order,aisle_id:department) %>% 
  group_by(aisle_id,aisle) %>%  
  summarise(
    total=n()
  ) %>% 
  arrange(
   -total
  )
```

### 1.b
There are 134 aisles in total and the most items are ordered from aisle 83, the fresh vegetables aisle.

```{r part 1c}
c_dept = dept %>%
  as.data.frame() %>% 
  filter(total>10000) %>% 
  arrange(aisle_id)

c_dept %>% 
  ggplot(aes(x = total, y = aisle))+
  geom_point()
```

```{r part 1d}
baking=instacart %>% 
  group_by(aisle_id,aisle,product_name) %>% 
  filter(
    aisle=="baking ingredients"
    ) %>% 
  summarise(
    total=n()
  ) %>% 
  arrange(
    -total
  ) %>% 
  head(3)

dog_food=instacart %>% 
  group_by(aisle_id,aisle,product_name) %>% 
  filter(
    aisle=="dog food care"
    ) %>% 
  summarise(
    total=n()
  ) %>% 
  arrange(
    -total
  ) %>% 
  head(3)

pack_veg_fruits=instacart %>% 
  group_by(aisle_id,aisle,product_name) %>% 
  filter(
    aisle=="packaged vegetables fruits"
    ) %>% 
  summarise(
    total=n()
  ) %>% 
  arrange(
    -total
  ) %>% 
  head(3)

d_table = bind_rows(baking,dog_food,pack_veg_fruits) %>% 
  rename(total_ordered=total) %>% 
knitr::kable(digits = 1)
```

`r d_table`

```{r part 1e}
pink_lady = instacart %>% 
  select(product_name,order_dow,order_hour_of_day) %>% 
  filter(
    product_name=="Pink Lady Apples"
    ) %>%
  group_by(product_name,order_dow) %>% 
  summarise(
    avg_hour_ordered=mean(order_hour_of_day)
  ) %>% 
  pivot_wider(
    names_from = order_dow,
    values_from = avg_hour_ordered
  )

ice_cream = instacart %>% 
  filter(
    product_name=="Coffee Ice Cream"
    ) %>% 
  select(product_name,order_dow,order_hour_of_day) %>% 
  group_by(product_name,order_dow) %>% 
  summarise(
    avg_hour_ordered=mean(order_hour_of_day)
  ) %>% 
  pivot_wider(
    names_from = order_dow,
    values_from = avg_hour_ordered
  )

e_table = bind_rows(pink_lady,ice_cream) %>% 
  rename(Monday="0",
         Tuesday="1",
         Wednesday="2",
         Thursday="3",
         Friday="4",
         Saturday="5",
         Sunday="6",
         Product="product_name") %>%
knitr::kable(digits = 1)

```

`r e_table`

## Problem 2

```{r}
library(p8105.datasets)
data("brfss_smart2010")
```

```{r problem 2 data cleaning}
brfss_cleaning=brfss_smart2010 %>% 
  janitor::clean_names() %>% 
  filter(topic == "Overall Health") %>% 
  rename(state = locationabbr,location=locationdesc) %>% 
  mutate(
    response=factor(response,levels = c("Poor","Fair","Good","Very good","Excellent")),
  ) 
```

```{r problem 2a response code}
brfss_2002 =  brfss_cleaning %>% 
  filter(year==2002) %>% 
  group_by(state) %>% 
  summarise(
    observed = n()/5
  ) %>% 
  filter(observed>=7)

brfss_2010 =  brfss_cleaning %>% 
  filter(year==2010) %>% 
  group_by(state) %>% 
  summarise(
    observed = n()/5
  ) %>% 
  filter(observed>=7)
```

`r pull(brfss_2002,state)` were the states with 7 or more than observation sites in 2002.

`r pull(brfss_2010,state)` were the states with 7 or more than observation sites in 2010.

```{r problem 2b plot}
exc_health=brfss_cleaning %>% 
  filter(response=="Excellent") %>% 
  group_by(year,state) %>%
  summarise(
    avg_data_value=mean(data_value,na.rm = TRUE)
  )

exc_health %>%   
  ggplot(aes(x=year,y=avg_data_value,color=state))+
  geom_line(alpha=.3,aes(group=state))+
  theme(legend.position="none")

```

```{r problem 2c}
nyc_data_2006=brfss_cleaning %>% 
  filter(state=="NY",year=="2006") %>% 
  group_by(response)

nyc_data_2010=brfss_cleaning %>% 
  filter(state=="NY",year=="2010") %>% 
  group_by(response)

nyc_data=bind_rows(nyc_data_2006,nyc_data_2010) %>% 
  group_by(year,response) %>% 
  summarise(
    data_avg=mean(data_value)
  )

nyc_data %>% 
  ggplot(aes(x=response,y=data_avg))+
  geom_col()+
  facet_grid(~year)+
  labs(
    x="Response",
    y="Number of Responses",
    title="Survey Data in NYS" 
  )
```

## Problem 3

```{r problem 3 tidying}
accel=read_csv(file="./accel_data.csv")

accel_mod=accel %>% 
  janitor::clean_names() %>% 
  mutate(
    weekday_vs_weekend = case_when(
      day == "Monday" ~ "Weekday",
      day == "Tuesday" ~ "Weekday",
      day == "Wednesday" ~ "Weekday",
      day == "Thursday" ~ "Weekday",
      day == "Friday" ~ "Weekday",
      day == "Saturday" ~ "Weekend",
      day == "Sunday" ~ "Weekend",
  )) %>% 
  select(week,day_id,day_of_the_week = day,weekday_vs_weekend,everything()) %>% 
  pivot_longer(
    activity_1:activity_1440,
    names_to = "activity_num", 
    values_to = "activity_count"
    )
```

The cleaned dataset is a data set with `r ncol(accel_mod)` variables and `r nrow(accel_mod)` observations. The variables of this dataframe are `r colnames(accel_mod)`.




